A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-21 paper.tex

We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfy the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align}
S_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
S_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right). \label{eq:gaugeI2}
\end{align}

@@

\begin{theorem}
Fix the twisting datum $\alpha = \alpha_n$. The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$. Moreover, the equivalence is $\MU(2)$-equivariant.
\label{thm:4d2holomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}+ \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}+ a \\
B&\rightsquigarrow B+ b \\
\rho&\rightsquigarrow \rho+ \Tilde{\chi} \\
\psi & \rightsquigarrow \psi+ \varsigma . \\
\end{align*}

@@

\begin{theorem} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized BF theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

\begin{proof}
By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\mr U(1)$-equivariant by our choice of a twisting homomorphism.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory, or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory. 
The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.

\vspace{-10pt}
\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
The fields are:
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
 \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
 \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
 \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  
 In this case $Q$ is minimal, with 2 invariant directions.  
 Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence.
They admit a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading defined by a homomorphism $\alpha \colon \U(1) \to G_R$.
 \item Rank 2. Such supercharges are topological.  
A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  
The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.  
We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
\begin{enumerate}
\item
An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
\item
A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
This twist is only $\ZZ/2\ZZ$-graded
\end{enumerate}
\end{itemize}

@@

\begin{lemma} \label{3d_4_orbits_lemma}
A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.  Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
\end{lemma}

\begin{proof}
Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supersymmetry algebra.
The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.  
This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.  The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor. 
This is the $A$-twist in our classification above.

A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.  This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.  
\end{proof}

\subsubsection{Minimal Twist}
\label{sect:3d_4_minimal_twist}
Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.

There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.

This twist also admits the following twisting datum.
To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.  The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.  Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.  Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.

\begin{theorem} \label{3d_4_minimal_twist_thm}
The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

\begin{proof}
The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.  This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
\end{proof}

\subsubsection{Topological $A$-Twist}
\label{sect:3d_4_A_twist}
Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. Consider the 4-dimensional spacetime $V_\RR=L\times N$. Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions. Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist. Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.

\begin{theorem}
The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\label{3d_4_A_twist_thm}
\end{theorem}

\begin{corollary}
The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
\end{corollary}

@@

The classification of twists therefore takes the following form.  We identify how the two orbits of rank 2 supercharges arise by dimensional reduction from 4d $\mc N=4$ by forgetting the supertranslation action down to 3d $\mc N=4$ (this may partially break the R-symmetry, but this is enough to distinguish the two classes of twisted theory).
\begin{itemize}
 \item Rank 1.  In this case $Q$ is minimal, with 2 invariant directions.  Such supercharges come from the $\mc N=2$ supersymmetry algebra.  They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $A$-twist.  These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.  The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.  It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $B$-twist.   These twists are topological, and come from the $\mc N=4$ supersymmetry algebra. The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.  It admits a twisting homomorphism $\phi \colon \Spin(3;\RR) \to G_R$.
\end{itemize}

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ supersymmetric Yang--Mills theory, viewed as an $\cN=4$ supersymmetric theory, coincides with the 3d $\cN=4$ supersymmetric Yang--Mills theory with matter valued in the symplectic representation $U = T^*\gg$.  
Alternatively, it is obtained by dimensional reduction of 4d $\mc N=4$ supersymmetric Yang--Mills theory.

\begin{theorem}  \label{3d_8_minimal_twist_thm}
The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

\begin{proof}
By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to the desired generalized BF theory.
\end{proof}

@@

\subsubsection{Topological $A$-Twist}
\label{sect:3d8A_Twist}
From Theorem \ref{3d_4_A_twist_thm}, using the same argument, we obtain the following statement.

\begin{theorem} \label{3d_8_A_twist_thm}
The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\end{theorem}
\brian{Need to explain what happened to $\Sect$}

\begin{corollary}
The topological $A$-twist of 3d $\cN=8$ super Yang-Mills is perturbatively trivial.
\end{corollary}

\subsubsection{Topological $B$-Twist}
\label{sect:3d8B_Twist}
From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.

\begin{theorem} \label{3d_8_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. %Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}
\brian{Need to explain what happened to $\Sect$}

>>>>

We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $S_{\gauge}^{(1)}, S_{\gauge}^{(2)}, \dots$, where $S_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $S_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align}
S_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
S_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right). \label{eq:gaugeI2}
\end{align}

@@

\begin{theorem}
Fix the homomorphism $\alpha = \alpha_n$. The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$. Moreover, the equivalence is $\MU(2)$-equivariant.
\label{thm:4d2holomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}+ \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}+ a \\
B&\rightsquigarrow B+ b \\
\rho&\rightsquigarrow \rho+ \Tilde{\chi} \\
\psi & \rightsquigarrow \psi+ \varsigma . \\
\end{align*}

@@

\begin{theorem} \label{3d_minimal_twist_thm}
The minimal twist of the 3d $\cN=2$ super Yang--Mills theory with Lie algebra $\fg$ with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover, this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

\begin{proof}
By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$. By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of the holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
Next, consider the 3d $\mc N=4$ supersymmetric Yang--Mills theory with matter valued in a symplectic $G$-representation $U$. The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the vector representation.

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  
 In this case $Q$ is minimal, with 2 invariant directions.  
 Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence. They admit a twisting homomorphism and a $\ZZ$-grading.
 \item Rank 2. Such supercharges are topological.  
A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  
The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation. We refer to these as the $A$-twist and the $B$-twist, distinguished by whether they admit a $\ZZ$-grading:
\begin{enumerate}
\item
An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
\item
A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
This twist is only $\ZZ/2\ZZ$-graded.
\end{enumerate}
\end{itemize}

@@

\begin{lemma} \label{3d_4_orbits_lemma}
A rank $(2,0)$ square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.  Likewise, a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
\end{lemma}

\begin{proof}
Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supersymmetry algebra.
The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.  
This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.  This supercharge admits a compatible homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor. This is the $A$-twist in our classification above.

A rank $(1,1)$ supercharge induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.  This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.  
\end{proof}

\subsubsection{Minimal Twist}
\label{sect:3d_4_minimal_twist}
There is a unique twisting homomorphism $\phi \colon \MU(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\MU(1) \subset \MU(2)$.

To incorporate the $\ZZ$-grading, we use the homomorphism $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$. This homomorphism coincides with the dimensional reduction of $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. The corresponding $\U(1)$-action on the 3d auxiliary space $W$ under $\alpha$ coincides with the $\U(1)$-action on the 4d auxiliary space $W_4$ under the isomorphism $W\cong W_4\oplus W_4^*$. Indeed, both have weights $(1,1,-1,-1)$.  Therefore, our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.  Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.

\begin{theorem} \label{3d_4_minimal_twist_thm}
The minimal twist of 3d $\cN=4$ super Yang--Mills on $\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\Sect(\CC \times \RR_{\mr{dR}}, (U \otimes K^{1/2}_\CC) \ham \gg))$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}
\begin{proof}
The statement follows by applying the dimensional reduction (Theorem \ref{prop:BFholomorphicreduction}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of the 4d $\mc N=2$ super Yang--Mills theory on $\CC\times\CC$, where we dimensionally reduce along the projection $\Re\colon\CC\rightarrow \RR$ in the second factor.
\end{proof}

\subsubsection{Topological $A$-Twist}
\label{sect:3d_4_A_twist}
Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. Consider the 4-dimensional spacetime $V_\RR=L\times N$. Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions. Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological $A$ twist. Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.

\begin{theorem}
The twist of the 3d $\cN=4$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(\CC \times \RR_{\mr{dR}}, ((U \otimes K^{1/2}_\CC)\ham \gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\label{3d_4_A_twist_thm}
\end{theorem}

\begin{corollary}
The topological $A$ twist of the 3d $\cN=4$ super Yang--Mills theory is perturbatively trivial.
\end{corollary}

@@

The classification of twists therefore takes the following form.
\begin{itemize}
 \item Rank 1.  In this case $Q$ is minimal, with 2 invariant directions.  Such supercharges come from the $\mc N=2$ supersymmetry algebra.  They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading.
 \item Rank 2 twists. These twists are topological, and come from the $\mc N=4$ supersymmetry algebra. They admit a twisting homomorphism from $\Spin(3, \RR)$ and a $\ZZ$-grading. There are two such:
 \begin{enumerate}
 \item $A$-twist (the generic rank 2 orbit).
 \item $B$-twist (the special rank 2 orbit).
 \end{enumerate}
\end{itemize}

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}

The 3d $\cN=8$ supersymmetric Yang--Mills theory is obtained by a dimensional reduction of the 4d $\mc N=4$ supersymmetric Yang--Mills theory. Therefore, from Theorem \ref{thm:4d4holomorphictwist} we obtain the following statement.

\begin{theorem}  \label{3d_8_minimal_twist_thm}
The minimal twist of the 3d $\cN=8$ super Yang--Mills theory on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

@@

\subsubsection{Topological Twists}

Consider the dimensional reduction of the family $Q_t$ of rank $(2, 2)$ square-zero supercharges in the 4d $\cN=4$ supersymmetry algebra from Section \ref{sect:4dqgltwist}. Since this is a family of topological supercharges in 4 dimensions, it dimensionally reduces to a family of topological supercharges in 3 dimensions.

\begin{theorem}
The twist of the 3d $\cN=8$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $T^*[-1]\map(\RR^3_{\mathrm{dR}}, B\fg_{\Hod})$. Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
\label{thm:3d8Hodgetwist}
\end{theorem}
\begin{proof}
The claim follows by dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) from the corresponding statement in 4 dimensions (Theorem \ref{thm:4d422Hodgetwist}) which calculates the twist of the 4d $\cN=4$ super Yang--Mills theory with respect to that family to be $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$.
\end{proof}

As we see from Theorem \ref{thm:3d8Hodgetwist}, at $t\neq 0$ the twist is perturbatively trivial while at $t=0$ it is not. By Lemma \ref{lm:3dN8twoorbits} there are only two orbits of topological supercharges, so the case $t\neq 0$ (the generic orbit) must be the $A$-twist and the case $t=0$ (the special orbit) must be the $B$-twist.

\begin{cor}
The topological $A$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively trivial.
\label{cor:3dN8Atwist}
\end{cor}

\begin{cor}
The topological $B$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively equivalent to $T^*[-1]\map(\RR^3_{\mathrm{dR}}, \fg/\fg)$. Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
\label{cor:3dN8Btwist}
\end{cor}
